Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-17 Ben_Manuscripts/transport/Supporting_Information.tex
Edits to draft

>>>>

  \section{Pore Region Definition}\label{section:pore-region}

  We performed a sensitivity analysis in order to determine the radial 
  cut-off that maximizes the difference in hop lengths in and out of 
  the pore region. We varied the location of the cut-off defining the
  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
  varied the cut-off in increments of 0.1 from 0.7 to 0.8 in order to
  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
  Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.1 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}
